---
output: github_document
---

```{r setup, include=FALSE}
# README.Rmd is processed by the developer of the package
# to create a README.md or README.html for the user of the package.
# The README should be processed as last step in the development process.
# This means that we should load here the latest version of the package.
# So that is what we will do below.
#
# Also when we are developing the package and
# in parallel writing the README, we want to use for the
# README the latest version of the package.
#
# Load the latest version of the package that is under development.
if (requireNamespace("devtools", quietly = TRUE) &&
  file.exists("evalstratified.Rproj")) {
  devtools::load_all(".")
} else {
  # Error! Break off knitting process.
  stop("README evalstratified: no evalstratified.Rproj in current directory.")
}

# Laad de library expliciet in voor de inline code verderop in het document
library(evalstratified)

# Set global knitr options for all subsequent chunks
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",

  # Route messages, warnings and errors to the R console, i.e. the developer.
  # Not to the resulting document, i.e. the reader.
  message = FALSE,
  warning = FALSE,
  error = FALSE
)
```

# evalstratified

< !--badges:start- ->
[![R - CMD - check](https://github.com/cfjdoedens/evalstratified/actions/workflows/
R - CMD - check.yaml/badge.svg
)](
https://github.com/cfjdoedens/evalstratified/actions/workflows/
R - CMD - check.yaml
)
[![Deploy Shiny App](
https://github.com/cfjdoedens/evalstratified/actions/workflows/
deploy - shiny.yaml/badge.svg
)](
https://github.com/cfjdoedens/evalstratified/actions/workflows/
deploy - shiny.yaml
)
< !--badges:end- ->

The goal of evalstratified is to make an estimate of the
error fraction of a set of monetary files.
This based on a global level of certainty, a level of certainty per file, and on error fractions
found in sampled items of each of these
files.

## Installation

You can install the development version of evalstratified from
[GitHub](https://github.com/) with:

```{r install, eval = FALSE, echo = TRUE}
if (!requireNamespace("devtools", quietly = TRUE)) {
install.packages("devtools")
}
devtools::install_github("cfjdoedens/evalstratified")
```

## Example

Steekproef1 is gebaseerd op een zekerheid van 95% omdat
ihr, ibr en car alledrie op hoog (H) staan. We kunnen dit ook narekenen met `haro_nog_nodige_zekerheid(ihr = "H", ibr = "H", car = "H")`. Dit levert inderdaad `r haro_nog_nodige_zekerheid(ihr = "H", ibr = "H", car = "H")` op. De materialiteit is 2%.
Het betreft 100 miljoen euro.
Om te bepalen hoeveel posten we moeten trekken voor
steekproef1 gebruiken we `drawsneeded::drawsneeded(0, 0.02, cert = 0.95)`. Resultaat:`r drawsneeded::drawsneeded(0, 0.02, cert = 0.95)`.
Na trekken en evalueren blijkt er 1 post fout te zijn.

Bij steekproef2 staan ihr en ibr allebei op laag en alleen car staat op hoog. We berekenen de benodigde zekerheid met `haro_nog_nodige_zekerheid(ihr = "L", ibr = "L", car = "H")`. Dit levert `r haro_nog_nodige_zekerheid(ihr = "L", ibr = "L", car = "H")` op. Het betreft ook 100 miljoen euro en een materialiteit van ook 2%.
Voor steekproef2 bepalen we vervolgens het aantal te trekken posten met `drawsneeded::drawsneeded(0, 0.02, cert = 0.64)`. Resultaat:`r drawsneeded::drawsneeded(0, 0.02, cert = 0.64)`. Na trekken en evalueren blijkt geen enkele post hiervan fout te zijn.

```{r example}
library(evalstratified)

example <- tribble(
~ naam,
~ waarde_laag,
~ n_laag,
~ k_laag,
~ ihr,
~ ibr,
~ car,
~ materialiteit,
~ fout_hoog,
~ goed_hoog,
~ n_hoog,
~ n_totaal,
~ waarde_hoog,
~ waarde_populatie,
"populatie1",
100000000,
148,
1,
"H",
"H",
"H",
0.02,
0,
0,
0,
148,
0,
100000000,
"populatie2",
100000000,
50,
0,
"L",
"L",
"H",
0.02,
0,
0,
0,
50,
0,
100000000
)

r <- eval_stratified(steekproeven = example, zekerheid = 0.95)
r
```
## Live version

On https://cfjdoedens.shinyapps.io/evalstratified/one can find a live version of this package.

## Ideas for further development

1. Add to live version the option to choose between

- Dutch text + European number notation, or
- English text + European number notation, or
- English text + English number notation

1. Add informative texts to the various numbers that can be filled in, or are produced. This info appears by pressing little
icons ("i" or so) near the subject matter.
